Sex-Specific Evolution of the Meiotic Recombination Rate

### 2020-06-23 doc/MS_v3.Rmd
finalized v3 of MS, sent to bret

---
title: 'Sex-Specific Evolution of the Meiotic Recombination Rate'
date: '`r Sys.Date()`'
author: "April L. Peterson, Bret A. Payseur"
output:
  word_document:
  pdf_document:
    includes:
      in_header: header.tex
  html_document:
always_allow_html: yes
bibliography: refs_Main_Report.bib
csl: elife.csl
---

>>>>

---
title: 'Sex-Specific Evolution of the Meiotic Recombination Rate'
date: '`r Sys.Date()`'
author: "April L. Peterson, Bret A. Payseur"
output:
  html_document:
  pdf_document:
    includes:
      in_header: header.tex
  word_document:
always_allow_html: yes
bibliography: refs_Main_Report.bib
csl: elife.csl
---
